---
title: "Getting google scholar informations with R"
author: "by [Yan Holtz](https://github.com/holtzy/) - `r format(Sys.time(), '%d %B %Y')`"
output:
  epuRate::epurate:
    toc: FALSE
    code_folding: "show"
---

<br><br>

> This documents provides a few line of codes to retrieve information from the google scholar API.



# Load libraries
***

A few library are needed for this work, notably the scholar library that allows to call the google scholar API.
```{r, warning=FALSE, message=FALSE}
library(rmarkdown)
library(scholar)      # To request data from google scholar.
library(tidyverse)    # What do you do without?
library(hrbrthemes)
library(DT)
```


# Basic information about a researcher
***

In this document we will study the publication of my Colleague [Vincent Ranwez](https://sites.google.com/site/ranwez/). His google scholar ID is `WLaQnegAAAAJ&hl`
```{r}
# Define the google scholar id
id <- 'WLaQnegAAAAJ&hl'       # Vincent Ranwez
```

Get his profile and print his name
```{r}
# Make an object called l with all the basic info of this id: name, affiliation, # of cites, H index, homepage ...
l <- get_profile(id)
name=l$name
tmp=strsplit(name, " ") %>% unlist()
last_name = tmp[length(tmp)]

# Show the last name
last_name
```

# Number of citation per year:
***

This allows to reproduce the chart on the right of the google scholar page: 
```{r, fig.align="center", fig.width=7}
# get the info
citation = get_citation_history(id)

# plot it
citation %>% 
  ggplot( aes(x=year, y=cites)) + 
    geom_segment( aes(x=year, y=0, xend=year, yend=cites), color="grey") +
    geom_point( size=4, col="#69b3a2") + 
    theme_ipsum()
```




# List of publications
***
Here is the detail of the publication:
```{r, warning=FALSE}
data=get_publications(id)
datatable(data, rownames = FALSE,  options = list(pageLength = 4))
```



# Involved Journals?
***
In total, `r nrow(data)` paper have been published in `r length(unique(tolower(data$journal)))` different journals. Here is an overview of the most frequent journals.
```{r, fig.width=8}
table(tolower(data$journal)) %>% as.data.frame() %>% filter(Freq>1) %>% arrange(Freq) %>% mutate(Var1=factor(Var1, Var1)) %>%
  ggplot(aes(x=Var1, y=Freq)) +
    geom_bar(stat="identity", width=0.5, fill="#69b3a2") +
    coord_flip() +
    xlab("") +
    theme_ipsum()
```


# Number of paper per year?
***

```{r, fig.align="center", fig.width=7, warning=FALSE, message=FALSE}
data %>% 
  ggplot(aes(x=year)) + 
    geom_bar( fill="#69b3a2") +
    theme_ipsum()
```


# Connection matrix of co-authors
***

Since the list of authors is available for each publication, it is possible to compute an adjacency matrix providing the relationship between every coauthors.
```{r}
# Compute all the pairs observed in the dataset:
return_all_pair=function(x){
  tmp = x  %>% gsub(", \\.\\.\\.", "", .) %>% strsplit(", ")  %>% unlist()
  if(length(tmp)>1){
    tmp = t(combn(tmp, 2))
  }
  return(tmp)
}
list_of_pairs = lapply( data$author, return_all_pair ) 
connect = do.call(rbind, list_of_pairs) %>% unique()
colnames(connect)=c("from", "to")

# Delete the target author from this list
connect = connect %>% 
  as.data.frame() %>% 
  filter( !grepl(last_name, from, ignore.case = TRUE) ) %>% 
  filter( !grepl(last_name, to, ignore.case = TRUE) )

# Change format to adjacency matrix and save it
adjacency <- connect %>% 
  mutate(value=1) %>%
  spread(key = to, value = value)
write.table(adjacency, file="DATA/ranwez_adj.csv", row.names=F)
```

<br>

In total, `r c( as.character(connect$from), as.character(connect$to)) %>% unique() %>% length()` co-authors have been found. But who are the most frequent coauthors?





```{r, fig.align="center", fig.width=7, fig.height=9, warning=FALSE, message=FALSE}
c( as.character(connect$from), as.character(connect$to)) %>% 
  table() %>% 
  as.data.frame() %>% 
  filter(Freq>5) %>% 
  arrange(Freq) %>% 
  mutate(Var1=factor(.,.)) %>%
    ggplot(aes(x=Var1, y=Freq)) +
      geom_segment( aes(x=Var1, y=0, xend=Var1, yend=Freq), color="grey") +
      geom_point( size=4, col="#69b3a2") + 
      coord_flip() +
      xlab("") +
      theme_ipsum() +
      ylab("Number of publication together")
```




#- Visualization
***

The adjacency matrix of co-authors connection is a dataset example used in the [data to viz](http://www.data-to-viz.com) project. Check the [dedicated webpage](http://www.data-to-viz/story/13_AdjacencyMatrix.html) for a few visualization made with this matrix.









